%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Journal Article
% LaTeX Template
% Version 1.3 (9/9/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[twoside]{article}

\usepackage{lipsum} % Package to generate dummy text throughout this template

\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics

\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage{multicol} % Used for the two-column layout of the document
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
\usepackage{hyperref} % For hyperlinks in the PDF

\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{6.s062 Final Project Proposal $\bullet$ March 2016} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

%----------------------------------------------------------------------------------------
% TITLE SECTION
%----------------------------------------------------------------------------------------

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Secure BLE-Based Authentication using Sensor Augmentation}}

\author{
\large
\textsc{Austin Freel, Andrew Titus}\\[2mm] % Your name
\normalsize Massachusetts Institute of Technology \\ % Your institution
\normalsize [\href{mailto:afreel@mit.edu}{afreel}, \href{mailto:atitus@mit.edu}{atitus}]@mit.edu % Your email address
\vspace{-5mm}
}
\date{}

%----------------------------------------------------------------------------------------

\begin{document}

\maketitle % Insert title

\thispagestyle{fancy} % All pages have headers and footers

%----------------------------------------------------------------------------------------
% ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\begin{multicols}{2} % Two-column layout throughout the main article text

\section{Introduction}

\lettrine[nindent=0em,lines=3]{M}any multi-factor authentication schemes using external
hardware exist, but few utilize the existing Bluetooth Low Energy (BLE) and sensor hardware
on people's mobile devices. This lack of ubiquity can lead to significant ``friction'' in
users - that is, users experience a level of frustration every time they need to use a
separate device that can often lead to users opting for less secure but easier to use methods.
Fortunately, most mobile devices manufactured in the past few years contain hardware that
enables BLE and various sensors to be utilized for wireless communications and data collection.
This leads us to propose that a ``low-friction'' system can be built for existing mobile
hardware that guarantees the same level of security for multi-factor authentication.

%------------------------------------------------

\section{Methodology}

Many Bluetooth-enabled peripherals (including mobile devices) have the ability to support
encrypted communication. We will build our system on iOS, as the operating system requires
that all remote devices connected to it support encrypted pairing connections
(https://support.apple.com/en-us/HT204387). We will start out by developing a pair of iOS
9 applications, one of which will function as a normal user and one of which will function
as the BLE peripheral to which to send encrypted credentials. This will enable us to test
the pairing and authentication processes without using external hardware for peripherals
during testing. Then, we plan to replace this BLE peripheral iPhone with an external
hardware device, such as the Anthill or a custom-built Bluetooth peripheral (perhaps
a 6.115 project by Andrew).

The setup of the pairing connection will be done by standard Apple guidelines for connecting
Bluetooth devices. Authentication methods, however, are much more flexible and wide-ranging.
We will initially start with a simple one-factor authentication system, such as a username/password
combination or certificate-based system. Then, we will move into multi-factor authentication
schemes which are augmented by internal sensor data, such as gestures. We also hope to make the
system more robust to spurious authentications by using sensor data as well. For example, in the
use case of the BLE peripheral being a door lock, this would prevent users from unlocking a door
if they are simply walking by it.

%------------------------------------------------

\section{Plan and Schedule}

\begin{table}[H]
\caption{Example table}
\centering
\begin{tabular}{llr}
\toprule
\multicolumn{2}{c}{Name} \\
\cmidrule(r){1-2}
Scheisse 1 & Scheisse 2 & Scheisse 3 \\
\midrule
Hello 1 & Hello 2 & Hello 3 \\
Hello 4 & Hello 5 & Hello 6 \\
\bottomrule
\end{tabular}
\end{table}

Bob Loblaw

\begin{equation}
\label{eq:emc}
e = mc^2
\end{equation}

Bob Loblaw

%------------------------------------------------

\section{Resources and Requirements}

\subsection{Subsection One}

Bob Loblaw

\subsection{Subsection Two}

Bob Loblaw

\end{multicols}

\end{document}
